### 2012-01-26 docs/notes.tex
Add discussion about extensions of the model.

\section{Inference}

@@

To perform Gibbs sampling for a given cluster assignment $z_i$, we need to compute the likelihood for each possible assignment of $z_i$. 
This operation can be done in parallel, and only the portion of the likelihood involving the newly assigned cluster  need to be recomputed.  Computing the likelihood is then $O(T \cdot P \cdot 4N)$, though we essentially split this computation into $K^2$ pieces.

>>>>

\subsection{Extensions}
TODO: Explain difficulties in doing a mixed membership model.  As in the mixed-membership stochastic blockmodel \cite{Airoldi2008}, one could assume that each node has vector of probabilities, $\boldsymbol{\pi}_i$, for being assigned to each of the latent clusters.  In that case $z_i \sim \mbox{Categorical}(\boldsymbol{\pi}_i)$ for each node $i$ and $j$, and the ties are modeled via a stochastic blockmodel $\mbox{logit} p(y_{ij}) = \eta_{z_i,z_j}$.  One could extend our current framework by assuming that after the $m$th event, $i_m$ and $j_m$ redraw their latent class.

TODO: Discuss other variants, e.g. HMM that guides which latent class over time?

TODO: What about different clusters for senders and receivers (cite our KDD paper)?
\section{Inference}

@@

To perform Gibbs sampling for a given cluster assignment $z_i$, we need to compute the likelihood for each possible assignment of $z_i$. 
This operation can be done in parallel, and only the portion of the likelihood involving the newly assigned cluster  need to be recomputed.  Computing the likelihood is then $O(T \cdot P \cdot 4N)$ (though this computation is split into $K^2$ pieces) and must computed $N \cdot K$ times per Gibbs iteration.

\subsection{Approximate likelihood methods}

TODO: Discuss how one might sample the likelihood.  Cite Raftery paper.

TODO: Look at performance of this with respect to bias and performance measures.
